Timeliness of security updates for Android

### 2014-08-11 securityupdates.tex
Fill in some more placeholders

\input{dastats}
\input{avostats}
\newcommand{\percMarketShare}{XX\%~\cite{TODO}}
\newcommand{\daNumNetworkOperators}{XXX~[\S\ref{sec:results}]}
\newcommand{\daNumDevices}{\daNumOSDevices}
\newcommand{\daDeviceDays}{\daOSTotalDaysData}
% Num versions since \daStartDate
\newcommand{\bouncyCastleNumVersions}{A}
\input{countversions}
%\newcommand{\opensslNumVersions}{B}
\newcommand{\apacheLibsNumVersions}{C}
\newcommand{\apacheLibsNumLibs}{E}
%\newcommand{\linuxNumVersions}{D}

@@

\section{Introduction}
Android has \percMarketShare\ of the smartphone market and while the core development is controlled by Google there are about \daNumManufacturers\footnote{We computed this from the Device Analyzer~\cite{Wagner2013} data.} manufacturers which make devices which run Android.
Android receives regular updates  which add new features and fix bugs, including security vulnerabilities.
Many of these manufacturers customise the version of Android they ship and sometimes network operators (of which there are at least \daNumNetworkOperators) make further modifications.
Hence when Google produces an update to Android, the update may have to pass through the manufacturer and operator before reaching the user.
The manufacturer and operator have little financial incentive to perform this work as they have already sold the device.
Operators are cautious because if they ship a broken update then they will get many support requests which is expensive.
However there is ongoing legal action to force operators to ship updates for security vulnerabilities~\cite{Soghoian2013}.
Many phones are sold on long (18 month) contracts with monthly payments yet stop receiving updates before the end of the contract, while Windows XP could be purchased for a one off payment in October 2001 and received security updates until April 2014.
CESG, which advises the UK government on how to secure its computer systems, recommends picking Android devices from manufactures which are good at shipping security updates promptly~\cite{CESG2013} but it does not state which manufacturers are better.
We provide this information in~\S\ref{sec:security_scoring}.

@@

\section{Results}
\label{sec:results}
In this section we present the results of our analysis showing \daMeanInsecurityPerc\ of devices to have root vulnerabilities on average, nexus devices to be better than others, \daSecScoreBestmanufacturer\ to be the best manufacturer and ????. %TODO summarise our results
The Device Analyzer data used here was collected between \daStartDate\ and \daEndDate.
The \texttt{androidvulnerabilities.org} data was collected between \avoStartDate\ and \avoEndDate.
%TODO comparison of nexus update rates with iOS

>>>>

\input{dastats}
\input{avostats}
\newcommand{\percMarketShare}{XX\%~\cite{TODO}}
\newcommand{\daNumDevices}{\daNumOSDevices}
\newcommand{\daDeviceDays}{\daOSTotalDaysData}
% Num versions since \daStartDate
\newcommand{\bouncyCastleNumVersions}{A}
\input{countversions}
%\newcommand{\opensslNumVersions}{B}
\newcommand{\apacheLibsNumVersions}{C}
\newcommand{\apacheLibsNumLibs}{E}
%\newcommand{\linuxNumVersions}{D}

@@

\section{Introduction}
Android has \percMarketShare\ of the smartphone market and while the core development is controlled by Google there are about \daNumManufacturers\footnote{\label{foot:dadata}We computed this from the Device Analyzer~\cite{Wagner2013} data, see \S\ref{sec:results}.} manufacturers which make devices which run Android.
Android receives regular updates  which add new features and fix bugs, including security vulnerabilities.
Many of these manufacturers customise the version of Android they ship and sometimes network operators (of which there are at least \daNumOperators\textsuperscript{\ref{foot:dadata}}) make further modifications.
Hence when Google produces an update to Android, the update may have to pass through the manufacturer and operator before reaching the user.
The manufacturer and operator have little financial incentive to perform this work as they have already sold the device.
Operators are cautious because if they ship a broken update then they will get many support requests which is expensive.
However there is ongoing legal action to force operators to ship updates for security vulnerabilities~\cite{Soghoian2013}.
Many phones are sold on long (18 month) contracts with monthly payments yet stop receiving updates before the end of the contract, while Windows XP could be purchased for a one off payment in October 2001 and received security updates until April 2014.
CESG, which advises the UK government on how to secure its computer systems, recommends picking Android devices from manufactures which are good at shipping security updates promptly~\cite{CESG2013} but it does not state which manufacturers are better.
We provide this information in~\S\ref{sec:security_scoring}.

@@

\section{Results}
\label{sec:results}
In this section we present the results of our analysis showing \daMeanInsecurityPerc\ of devices to have root vulnerabilities on average, nexus devices to be better than others, \emph{\daSecScoreBestmanufacturer} to be the best manufacturer and \emph{\daSecScoreBestoperator} to be the best network operator. %TODO summarise our results
The Device Analyzer data used here was collected between \daStartDate\ and \daEndDate.
The \texttt{androidvulnerabilities.org} data was collected between \avoStartDate\ and \avoEndDate.
%TODO comparison of nexus update rates with iOS
